\toolname: file-based localization of numerical perturbations in data analysis pipelines

### 2020-04-11 paper.tex
A few fixes

We randomly selected 20 unprocessed subjects 
from the HCP data release S500 
available in \href{https://db.humanconnectome.org}{the ConnectomDB repository}. 
For each subject, available data consisted of 1 or 2 T1w images and 1 or 2 T2w images, with 
$256 \times 320 \times 320$ voxels of size $0.7 \times 0.7 \times 0.7$ mm.
Acquisition protocols and parameters are detailed in~\cite{van2013wu}.

@@

\subsection{Key findings}
\note{Greg}{feel free to ignore, but a peeve of mine is one heading directly following another. Is there some
kind of high-level summary you could put above this, or just omit the key-findings label?} \tristan{will do}
Linear and non-linear registration with FSL were found to
frequently lead to differences between results obtained with different
operating systems. This does not come as a surprise given the instabilities
associated with these processes. It also corroborates our previous findings
in~\cite{Glatard2015}, where fMRI pre-processing with FSL was found to vary across operating systems 
starting from the motion
correction step, a step that uses FSL's \flirt tool internally. It
would be relevant to investigate if the observed instability of
registration processes generalizes to other toolkits, or if it remains specific
to FSL. In view of the effect of small data perturbations in a variety of
toolboxes and processes, such as cortical surface extraction using
FreeSurfer and CIVET~\cite{Lewis2017-ll} or connectome estimation using
Dipy~\cite{kiar2019comparing}, it is probable that this observation
generalizes widely across toolboxes and requires a deeper investigation of
the stability of linear and non-linear registration.

@@

We presented \toolname, a tool to detect the source of numerical
differences in complex pipelines executed in different computational
conditions. \toolname leverages system-call interception through the
\reprozip tool, and therefore can be applied to the most complex pipelines
without requiring their instrumentation.

>>>>

We randomly selected 20 unprocessed subjects 
from the HCP data release S500 
available in \href{https://db.humanconnectome.org}{the ConnectomDB repository}. \tristan{Ali, I can't find any S500 
data release there, please confirm}
For each subject, available data consisted of 1 or 2 T1w images and 1 or 2 T2w images, with 
$256 \times 320 \times 320$ voxels of size $0.7 \times 0.7 \times 0.7$ mm.
Acquisition protocols and parameters are detailed in~\cite{van2013wu}.

@@

Results from our experiments provide insights on the reproducibility of
neuroimaging pipelines. They also allow us to evaluate the approach adopted
in \toolname.

\subsection{Key findings}
Linear and non-linear registration with FSL were found to
frequently lead to differences between results obtained with different
operating systems. This does not come as a surprise given the instabilities
associated with these processes. It also corroborates our previous findings
in~\cite{Glatard2015}, where fMRI pre-processing with FSL was found to vary across operating systems 
starting from the motion
correction step, a step that uses FSL's \flirt tool internally. It
would be relevant to investigate if the observed instability of
registration processes generalizes to other toolkits, or if it remains specific
to FSL. In view of the effect of small data perturbations in a variety of
toolboxes and processes, such as cortical surface extraction using
FreeSurfer and CIVET~\cite{Lewis2017-ll} or connectome estimation using
Dipy~\cite{kiar2019comparing}, it is probable that this observation
generalizes widely across toolboxes and requires a deeper investigation of
the stability of linear and non-linear registration.

@@

We presented \toolname, a tool to detect the source of numerical
differences in complex pipelines executed in different computational
conditions. \toolname leverages system-call interception through the
\reprozip tool, and therefore can be applied to the most complex pipelines
without requiring their instrumentation. \toolname is available at \url{https://github.com/big-data-lab-team/spot} under MIT license.
